Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/abstract.tex
update abstract

  We present \textit{Nail}, an interface generator that allows programmers to safely parse and
  generate protocols defined by a Parser-Expression based grammar. Nail uses a richer set of parser
  combinators that induce an internal representation, obviating the need to write semantic actions.
  Nail also introduces \textit{dependency fields} and \textit{stream transformations} that capture
  protocol features such as size and offset fields, check-sums and compressed data that are hard to
  express in existing protocol languages.

>>>>

\textit{Nail} is an interface generator that greatly reduces the
programmer effort for safely parsing and generating protocols defined
by a Parser-Expression based grammar.  Nail introduces several key
ideas to achieve its goal.  First, Nail uses the protocol grammar to
define not just the data format, but also the internal representation
of the data.  Second, Nail eliminates the notion of semantic actions,
used by existing parser generators, which reduces the expressive power
but allows Nail to both {\em parse} data formats and {\em generate}
them from internal representations, by maintaining a {\em semantic
bijection} between data formats and internal representation.  Third,
Nail introduces {\em dependency fields} and {\em stream transforms} to
capture protocol features such as size and offset fields, checksums,
and compressed data, which are impractical to express in existing
protocol languages.  Using Nail, we implement a complete DNS server in
C in under 300 lines of code and grammar, and a complete {\tt unzip}
program in C in 220 lines of code and grammar, demonstrating that Nail
makes it easy to parse complex real-world data formats.
